Technical Report

### 2018-06-22 fully-abstract-comp/technical-report.tex
Update and simplify a proof.

\begin{multline*}
  H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_,\gsigrets,\gsigcloss) \; \hat{W} =\\
  \left\{\npair{(\code,\code)} \middle|
    \begin{array}{l}
    \dom(\code) = [\aaddr,\baddr] \wedge \\
      (\dom(\code) \subseteq \ta \wedge \sigrets \subseteq \gsigrets \wedge \trust = \trusted) \vee \\
      \quad (\dom(\code)\mathrel{\#} \ta \wedge \sigrets = \emptyset \wedge \trust =\untrusted) \wedge \\
      \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code \wedge\\
      \forall a \in \dom(\code)\ldotp\\
      \quad\npair{(\code(a),\code(a))} \in \lrvg{\trust}(\purePart{\xi(\hat{W})})
    \end{array}
  \right\}
\end{multline*}

@@

\begin{lemma}
  \label{lem:codereg-not-read-write}
  If $n > 0$, $\dom(\code) \subseteq \ta$, $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$, $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ and $a \in \dom(\code)$ and $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\sigrets \neq \emptyset$, then
  \begin{itemize}
  \item $\npair{\{a\}} \not\in \readCond{\normal,W}$
    % \item $\npair{\{a\}} \not\in \writeCond{\normal,W}$
    % It seems unnecessary to show the part about the write condition as all non-no-perm permissions have read.
  \end{itemize}
\end{lemma}
\begin{proof}
  For the sake of contradiction assume $\npair{\{a\}} \in \readCond{\normal,W}$.
  Then there exists $S \subseteq \addressable{\lin, \pwheap}$ and $R : S \fun
  \powerset{\nats}$ such that
  \begin{itemize}
  \item $\biguplus_{r\in S} R(r) \supseteq A$
  \item $\forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$
  \end{itemize}
  We claim that $r_\code \in S$.
  If this is indeed the case, then we have $\pwheap(r_\code).H \nsubeq \stdreg{\dom(\code),\gc}{\pur}.H$ (we must have $R(r_\code) = \dom(\code)$ as the two regions couldn't be $\nequal$ otherwise).
  This means that for all $a \in \dom(\code)$ and $n' < n$ it must be the case that $\npair[n']{(\code(a),\code(a))} \in \lrv(W_a)$ for all $W_a$ that are compatible w.r.t.
  $\oplus$ and combine to be $W$.
  We know that $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ from which we can deduce $\npair{(\code,\code)} \in H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_) \; \xi^{-1}(W_\code)$ which in particular gives us $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code$.
  This in turns entails that for $\sigma \in \sigrets$ there exists some $a' \in \dom(\code)$ such that $\code(a') = \seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr}$ and $\sigma \in [\sigma_\baddr,\sigma_\eaddr]$.
  This means that for such a $\sigma$ and $a'$, it must be that case that
  $\npair[n']{(\seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr},\seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr})}
  \in \lrv(W_{a'})$ which gives us
  $\codereg{\sigrets,\sigcloss,\code,\gc}.H_\sigma  \; \sigma \nequal \lrv$
  contradicting Lemma~\ref{lem:codereg-Hsigma-not-lrv}.

  It remains to show $r_\code \in S$.
  To show this, we assume for contradiction that $r_\code \not\in S$.
  This means that there exists $r \neq r_\code$ such that $a \in R(r)$ and $\pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$.
  Because we know $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, it must be possible to split up $\ms_S$ in disjoint memory segments that each (paired with a target memory segment) satisfies exactly one region.
  In this case, both $r$ and $r_\code$ needs a memory segment that has $a$ in the domain which means that no such disjoint union can exist which gives us a contradiction.
\end{proof}

>>>>

\begin{multline*}
  H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_,\gsigrets,\gsigcloss) \; \hat{W} =\\
  \left\{\npair{(\code,\code)} \middle|
    \begin{array}{l}
    \dom(\code) = [\aaddr,\baddr] \wedge \\
      (\dom(\code) \subseteq \ta \wedge \sigrets \subseteq \gsigrets \wedge \sigcloss \subseteq \gsigcloss \wedge \trust = \trusted) \vee \\
      \quad (\dom(\code)\mathrel{\#} \ta \wedge \sigrets = \emptyset \wedge \trust =\untrusted) \wedge \\
      \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code \wedge\\
      \forall a \in \dom(\code)\ldotp\\
      \quad\npair{(\code(a),\code(a))} \in \lrvg{\trust}(\purePart{\xi(\hat{W})})
    \end{array}
  \right\}
\end{multline*}

@@

\begin{lemma}
  \label{lem:codereg-not-read-write}
  If
  \begin{itemize}
  \item $n > 0$
  \item $\dom(\code) \subseteq \ta$
  \item $\gc =
    (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\pwheap(r_\code) \nequal
    \codereg{\sigrets,\sigcloss,\code,\gc}$ 
  \item $a \in \dom(\code)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$
  \end{itemize}
  then
  \begin{itemize}
  \item $\npair{\{a\}} \not\in \readCond{\normal,W}$
    % \item $\npair{\{a\}} \not\in \writeCond{\normal,W}$
    % It seems unnecessary to show the part about the write condition as all non-no-perm permissions have read.
  \end{itemize}
\end{lemma}
\begin{proof}
  For the sake of contradiction assume $\npair{\{a\}} \in \readCond{\normal,W}$.
  Then there exists $S \subseteq \addressable{\lin, \pwheap}$ and $R : S \fun
  \powerset{\nats}$ such that
  \begin{itemize}
  \item $\biguplus_{r\in S} R(r) \supseteq A$
  \item $\forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$
  \end{itemize}
  Because we know $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, it must be possible to split up $\ms_S$ in disjoint memory segments that each (paired with a target memory segment) satisfies exactly one region.
  This means that only one region can govern address $a$, so that $r_\code \in S$

  It follows that $R(r_\code) = \dom(\code)$ and $\pwheap(r_\code).H \nsubeq \stdreg{\dom(\code),\gc}{\pur}.H$.
  From the fact that $\npair{(\code,\code)} \in \pwheap(r_\code).H~W'$ for some $W'$ with $W = W' \oplus \_$, and the fact that $\dom(\code)\subseteq \ta$, it also follows that $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$ and $\sigrets,\sigcloss\vdash_{\mathrm{comp-code}} \var{code}$.
  This now gives us a contradiction with Lemma~\ref{lem:codereg-H-not-subs-lrv}.
\end{proof}
